Douglas-complex fire smoke and cardiopulmonary morbidity

### 2017-11-06 r_scripts/analysis/oregon_cvd_pulm_results.Rmd
added table 1 function.

```{r health data import}
# importing case-crossover dataframes 
# SABA case-crossover will be imported first
# i can't find a lot of the files
#resp_path <- paste0("./"

# asthma
asthma_path <- paste0("./data/health/2017-oregon_casecross_asthma.csv")
asthma_df <- read_csv(asthma_path)

# cvd 
cvd_path <- paste0("./data/health/2017-oregon_casecross_cvd.csv")
cvd_df <- read_csv(cvd_path)
# had a warning message for cvd dataframe import; should check on this

@@

# I think purrr would be a good way to loop through a list of outcome dataframes
# bind dataframes in a list
outcome_df_list <- list(asthma_df, cvd_df)
```

@@

Descriptive table will go here.

```{r descriptive table}
# name list elements
names(outcome_df_list) <- c( 'Asthma', 'CVD')

# output row of summary numbers
test_row <- asthma_df %>% 
  filter(outcome == 1) %>%
  group_by(age_ind) %>% 
  summarise(n = n()) %>%
  mutate(age_cat = ifelse(age_ind == 0, "age_under15",
                    ifelse(age_ind == 1, "age_15to65", "age_over65")))

  forcats::as_factor(age_ind, levels = c("age_under15", "age_15to65", "age_over65"))

glimpse(test_ro)

descriptive_table <- outcome_df_list %>% 
  lmap()

?lmap

mtcars %>%
  split(.$cyl) %>%
  map(~ lm(mpg ~ wt, data = .x)) %>%
  map(summary) %>%
  map_dbl("r.squared")

# Use map_lgl(), map_dbl(), etc to reduce to a vector.
# * list
mtcars %>% map(sum)
# * vector
mtcars %>% map_dbl(sum)
```

>>>>

```{r health data import, message=F, warning=F}
# importing case-crossover dataframes 
# SABA case-crossover will be imported first
# i can't find a lot of the files
#resp_path <- paste0("./"

# asthma
asthma_path <- paste0("../../data/health/2017-oregon_casecross_asthma.csv")
asthma_df <- read_csv(asthma_path)

# cvd 
cvd_path <- paste0("../../data/health/2017-oregon_casecross_cvd.csv")
cvd_df <- read_csv(cvd_path)
# had a warning message for cvd dataframe import; should check on this

@@

# I think purrr would be a good way to loop through a list of outcome dataframes
# bind dataframes in a list
outcome_df_list <- list(asthma_df, cvd_df)

# name list elements in order I'd like to present in document
outcome_names <- c("SABA", "Respiratory", "Asthma", "COPD", "Pneumonia", 
  "Acute Bronchitis", "Cardiovascular Disease", "Arrhythmia", 
  "Cerebrovascular Disease", "Heart Failure", "Ischemic Heart Disease", 
  "Myocardial Infarction")

names(outcome_df_list) <- c( 'Asthma', 'CVD')
```

@@

Descriptive table will go here. Jingyang, I'll have you add the other dataframes to analyze. I provided an example of Asthma and CVD.

```{r descriptive table}
# creating a row calculation function
table1_fun <- function(data_list){
  # output of total n
  total_n <- data_list %>% 
    filter(outcome == 1) %>%
    summarise(total_n = n())

  # output row of summary numbers
  age_cat_n <- data_list %>% 
    filter(outcome == 1) %>%
    group_by(age_ind) %>% 
    summarise(n = n()) %>%
    mutate(age_cat = ifelse(age_ind == 0, "age_under15",
                      ifelse(age_ind == 1, "age_15to65", "age_over65")),
           # preserve factor order
           age_cat = parse_factor(age_cat, levels = age_cat)) %>% 
    select(-age_ind) %>% 
    spread(age_cat, n)
  # sex n
  sex_n <- data_list %>% 
    filter(outcome == 1) %>% 
    group_by(gender) %>% 
    summarise(n = n()) %>% 
    filter(gender != "U") %>% 
    spread(gender, n)
  # bind all rows together
  outcome_n_row <- bind_cols(total_n, age_cat_n, sex_n) %>% 
    mutate(perc_15 = round(age_under15/total_n,2), 
           perc_15to65 = round(age_15to65/total_n,2),
           perc_65 = round(age_over65/total_n,2),
           perc_F = round(F/total_n,2),
           perc_M = round(M/total_n,2)) %>% 
    select(total_n, age_under15, perc_15, age_15to65, perc_15to65, 
           age_over65, perc_65, F, perc_F, M, perc_M)
return(outcome_n_row)
} # end function

# outcome names
outcome_names <- names(outcome_df_list) %>% 
  data_frame() %>% 
  rename(outcome = ".")

# apply custom function to generate descriptive table
table_vals <- outcome_df_list %>% 
  # map to dataframe
  map_dfr(table1_fun) 
# descriptive table, bind outcome names and values
descriptive_table <- bind_cols(outcome_names, table_vals)

# output table
knitr::kable(descriptive_table, 
  caption = "Descriptive charactersitics of ED/urgent care visits")
```
